HBCC - DLPFC - FEATURECOUNTS - GRCh38 - CQN

### 2020-03-30 cmc-rnaseq-de/HBCC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
remove mds plot

plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID'))

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape=Dx, size=ageOfDeath))
p <- p + theme_bw() %+replace% theme(legend.position="top", plot.title = element_text(hjust=0.5, size = 15)) + ggtitle ("PCA MSSM/Penn/Pitt Cohort") + 
  guides(colour = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2),
         size = guide_legend(nrow = 2))
p
# p <- p + geom_text(aes(label= SampleID), size=4, hjust=0)

#MDS
tmp.mds <- dist(t(tmp))
mds <- cmdscale(tmp.mds)
#Plot MDS
plotdata <- data.frame(SampleID = rownames(mds),
                       MDS1= mds[,1],
                       MDS2= mds[,2])

plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID'))

p <- ggplot(plotdata, aes(MDS1,MDS2))
p <- p + geom_point(aes(shape=Dx, size=ageOfDeath))
p <- p + theme_bw() %+replace% theme(legend.position="top", plot.title = element_text(hjust=0.5, size = 15)) + ggtitle ("MDS MSSM/Penn/Pitt Cohort") + 
  guides(colour = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2),
         size = guide_legend(nrow = 2))
p
```
Tree based clustering of samples
```{r decompse.normalise.data.1, fig.height=6, fig.width=10, results='asis'}
# Eucledian tree based analysis
COVARIATES.tmp = data.matrix(COVARIATES[,c("Reported_Gender", "LibraryBatch", "Dx")])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0

>>>>

plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Dx.Tissue, c('Dx','Tissue'), sep = '_')

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=Institution, shape=Tissue, size=ageOfDeath))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(Tissue~.)
# p <- p + geom_text(aes(label= SampleID), size=4, hjust=0)
p
```
Tree based clustering of samples
```{r decompse.normalise.data.1, fig.height=6, fig.width=10, results='asis'}
# Eucledian tree based analysis
COVARIATES.tmp = data.matrix(COVARIATES[,c("Reported_Gender", "LibraryBatch", "Dx")])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
